### 2025-04-27 paper/paper.tex
Update paper.tex

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SUMO_RUNNING.png}
    \caption{Example of SUMO running in through SUMO-GUI}
\end{figure}

@@

Concretely, the helper function
\begin{verbatim}
build_mlp(input_dim, output_dim, hidden_layers):
    layers   = []
    prev     = input_dim
    for h in hidden_layers:
        layers.append(nn.Linear(prev, h))
        layers.append(nn.ReLU())
        prev = h
    layers.append(nn.Linear(prev, output_dim))
    return nn.Sequential(*layers)
\end{verbatim}
constructs the sequential network, allowing us to easily swap hidden layer sizes or depths via configuration.

Each intersection is managed by an instance of {\tt DQNAgent} (in policies.py), which maintains both an \emph{online} network and a \emph{target} network. At initialization, we load the target’s weights from the online network and set up an Adam optimizer (learning rate 0.001), a discount factor $\gamma=0.99$, and an $\varepsilon$‐greedy exploration schedule that decays $\varepsilon$ from 1.0 to 0.05 by a factor of 0.995 per learning step. Experiences are stored in a fixed‐capacity deque buffer (size 5,000), and we sample mini‐batches of 32 transitions once the buffer is sufficiently large. In each learn() call we compute the predicted Q‐values for state–action pairs, form TD‐targets via \(Q_{\mathrm{target}} = r + \gamma (1 - d)\max_{a'} Q_{\mathrm{target}}(s', a')\) and minimize the mean‐squared error between predictions and targets. After each gradient update, we decay $\varepsilon$, and every 100 updates we synchronize the target network with the online network. To scale this to multiple intersections, we wrap several {\tt DQNAgent} objects in {\tt MultiDQNAgent}, forwarding action selection, memory storage, and learning calls independently to each agent.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SUMO_RUNNING.png}
    \caption{Example of SUMO running in SUMO-GUI}
\end{figure}

@@

\newpage 
Concretely, the helper function
\begin{verbatim}
build_mlp(input_dim, output_dim, 
hidden_layers):
    layers   = []
    prev     = input_dim
    for h in hidden_layers:
        layers.append(nn.Linear(prev, h))
        layers.append(nn.ReLU())
        prev = h
    layers.append(nn.Linear(prev, 
    output_dim))
    return nn.Sequential(*layers)
\end{verbatim}
constructs the sequential network, allowing us to easily swap hidden layer sizes or depths via configuration.

Each intersection is managed by an instance of {\tt DQNAgent} (in policies.py), which maintains both an \emph{online} network and a \emph{target} network. At initialization, we load the target’s weights from the online network and set up an Adam optimizer (learning rate 0.001), a discount factor $\gamma=0.99$, and an $\varepsilon$‐greedy exploration schedule that decays $\varepsilon$ from 1.0 to 0.05 by a factor of 0.995 per learning step. Experiences are stored in a fixed‐capacity deque buffer (size 5,000), and we sample mini‐batches of 32 transitions once the buffer is sufficiently large. In each learn() call we compute the predicted Q‐values for state–action pairs, form TD‐targets via 
\[
Q_{\mathrm{target}} \;=\; r \;+\; \gamma\,(1 - d)\,\max_{a'} Q_{\mathrm{target}}(s', a')
\]
and minimize the mean‐squared error between predictions and targets. After each gradient update, we decay $\varepsilon$, and every 100 updates we synchronize the target network with the online network. To scale this to multiple intersections, we wrap several {\tt DQNAgent} objects in {\tt MultiDQNAgent}, forwarding action selection, memory storage, and learning calls independently to each agent.
